---
title: "Bubble Plot"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load packages & data

```{r load-packages, message=FALSE}
library(tidyverse)
library(nnet)
library(knitr)
library(tidyr)
library(plotly)
library(ggplot2)
library(dplyr)
```

```{r load-data}
LRRK2_gnomAD_frequencies_For_figure <- read_csv("LRRK2 gnomAD frequencies - For figure.csv")

data <- LRRK2_gnomAD_frequencies_For_figure %>% mutate("AA #" = as.numeric(LRRK2_gnomAD_frequencies_For_figure$`AA #`), "REVEL score" = as.numeric(LRRK2_gnomAD_frequencies_For_figure$`REVEL score`), Model = rownames(data))
```
```{r x}
data$pop = data$`pop freq. GnomAD`

data$pop[data$`pop freq. GnomAD` <= .000008] <- 0.0
data$pop[data$`pop freq. GnomAD` > .000008 & data$`pop freq. GnomAD` <= .000015] <- 1.0
data$pop[data$`pop freq. GnomAD` > .000015 & data$`pop freq. GnomAD` <= 0.00005] <- 2.0
data$pop[data$`pop freq. GnomAD` > 0.00005] <- 3.0
data$pop <- as.factor(data$pop)
```

```{r graph}
plot1 <- ggplot(data, aes(data$`AA #`, data$`REVEL score`, size = data$`pop freq. GnomAD`))  + geom_point(alpha = 0.5) + labs(x = "AA #", y = "REVEL score", title = "gnomAD REVEL Bubble Plot")  + scale_size(range = c(.1,25), breaks = c(.000008, .000015, 0.00005, 0.0001), guide = guide_legend(title = "Pop Freq"))

par(las = 3)

plot1
```
```{r graph1}
plot1 <- ggplot(data, aes(data$`AA #`, data$`REVEL score`, size = data$`pop freq. GnomAD`))  + geom_point(alpha = 0.5) + labs(x = "AA #", y = "REVEL score", title = "gnomAD REVEL Bubble Plot")  + scale_size_binned(range = c(.1,10), breaks = c(.000008, .000015, 0.00005, 0.0001), guide = guide_legend(title = "Pop Freq"))

par(las = 3)

plot1
```

{r graph1}
plot1 <- ggplot(data, aes(data$`AA #`, data$`REVEL score`, size = data$pop))  + geom_point(alpha = 0.5) + labs(x = "AA #", y = "REVEL score", title = "gnomAD REVEL Bubble Plot") + scale_size(range = c(1.0,10.0), breaks = c(0.0, 1.0, 2.0, 3.0), guide = guide_legend(title = "Pop Freq"))

par(las = 3)

plot1


```{r scale}
data$pop = data$`pop freq. GnomAD`

data$pop[data$`pop freq. GnomAD` <= .000008] <- 0.0
data$pop[data$`pop freq. GnomAD` > .000008 & data$`pop freq. GnomAD` <= .000015] <- 1.0
data$pop[data$`pop freq. GnomAD` > .000015 & data$`pop freq. GnomAD` <= 0.00005] <- 2.0
data$pop[data$`pop freq. GnomAD` > 0.00005] <- 3.0
data$pop <- as.factor(data$pop)
```

```{r}
plot1 <- ggplot(data, aes(data$`AA #`, data$`REVEL score`, size = data$`pop freq. GnomAD`))  + geom_point(alpha = 0.5) + labs(x = "AA #", y = "REVEL score", title = "gnomAD REVEL Bubble Plot")  + scale_size(range = c(.1,25), breaks = c(.000008, .000015, 0.00005, 0.0001), guide = guide_legend(title = "Pop Freq"))

par(las = 3)

plot1
```

{r graph1}
plot1 <- ggplot(data, aes(data$`AA #`, data$`REVEL score`, size = data$pop))  + geom_point(alpha = 0.5) + labs(x = "AA #", y = "REVEL score", title = "gnomAD REVEL Bubble Plot") + scale_size(range = c(1.0,10.0), breaks = c(0.0, 1.0, 2.0, 3.0), guide = guide_legend(title = "Pop Freq"))

par(las = 3)

plot1



{r graph2}
plot1 <- ggplot(data, aes(data$`AA #`, data$`REVEL score`, size = data$pop))  + geom_point(alpha = 0.5) + labs(x = "AA #", y = "REVEL score", title = "gnomAD REVEL Bubble Plot") + scale_size(range = c(1,10), breaks = c(0, 1, 2, 3), guide = guide_legend(title = "Pop Freq"))

par(las = 3)

plot1



### Julia's smart code


```{r new}
mybreaks <-c(0.002, 0.046, 0.23,1)
myfix <- c(10.0,20.0,60.0,100.0)

fig_plot <- data %>%
  arrange(desc(data$`pop freq. GnomAD`)) %>%
  mutate(freq = as.numeric(data$`pop freq. GnomAD`)) %>%
ggplot(aes(x = data$`AA #`, y = data$`REVEL score`, size = freq)) + scale_size(range = c(3.0,80.0), breaks = mybreaks, name = "Frequency") + geom_point(alpha = 0.5) + scale_y_continuous(name = "REVEL score", limits = c(0,1)) + scale_x_continuous(name = "Amino Acid Number", limits = c(0,2527)) + theme(legend.title = element_text(size = 20), legend.text = element_text(size = 20)) + xlab("Amino Acid Number") + ggsave("bubble_gnomAD.pdf", width = 35.0, height = 20.0, limitsize = FALSE)

par(las = 3)

fig_plot
```
