---
title: "Bubble Plot"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load packages & data

```{r load-packages, message=FALSE}
library(tidyverse)
library(nnet)
library(knitr)
library(tidyr)
library(plotly)
library(ggplot2)
library(dplyr)
library(htmlwidgets)
```

```{r load-data}
LRRK2_gnomAD_frequencies_For_figure <- read_csv("LRRK2 gnomAD frequencies - For figure.csv")

race_frequencies_Sheet <- read_csv("race frequencies - Sheet1.csv")

race_frequencies_Sheet1 <- race_frequencies_Sheet %>% mutate("AA #" = as.numeric(race_frequencies_Sheet$`AA #`), "REVEL score" = as.numeric(race_frequencies_Sheet$`REVEL score`), "Allele Frequency Latino" = as.numeric(race_frequencies_Sheet$`Allele Frequency Latino`))

race_frequencies_Sheet2 <- read_csv("race frequencies - Sheet1-2.csv")

race_frequencies_Sheet_final <- race_frequencies_Sheet2 %>% mutate("AA #" = as.numeric(race_frequencies_Sheet2$`AA #`), "REVEL score" = as.numeric(race_frequencies_Sheet2$`REVEL`))

REVEL_and_race <- read_csv("REVEL and Race Data - Sheet1.csv")
RevRace <- REVEL_and_race %>% mutate("REVEL score" = as.numeric(REVEL_and_race$`REVEL`), "Allele Frequency Latino" = as.numeric(REVEL_and_race$`Allele Frequency Latino`), "Allele Frequency African" = as.numeric(REVEL_and_race$`Allele Frequency African`), "Allele Frequency Ashkenazi Jewish" = as.numeric(REVEL_and_race$`Allele Frequency Ashkenazi Jewish`), "Allele Frequency East Asian" = as.numeric(REVEL_and_race$`Allele Frequency East Asian`),"Allele Frequency European (Finnish)" = as.numeric(REVEL_and_race$`Allele Frequency European (Finnish)`),"Allele Count Frequency European (non-Finnish)" = as.numeric(REVEL_and_race$`Allele Count Frequency European (non-Finnish)`),"Allele Frequency Other" = as.numeric(REVEL_and_race$`Allele Frequency Other`), "Allele Frequency South Asian" = as.numeric(REVEL_and_race$`Allele Frequency South Asian`))

data <- LRRK2_gnomAD_frequencies_For_figure %>% mutate("AA #" = as.numeric(LRRK2_gnomAD_frequencies_For_figure$`AA #`), "REVEL score" = as.numeric(LRRK2_gnomAD_frequencies_For_figure$`REVEL score`), Model = rownames(data))
```

, "Allele Frequency Latino" = as.numeric(race_frequencies_Sheet2$`Allele Frequency Latino`), "Allele Frequency African" = as.numeric(race_frequencies_Sheet2$`Allele Frequency African`), "Allele Frequency Ashkenazi Jewish" = as.numeric(race_frequencies_Sheet2$`Allele Frequency Ashkenazi Jewish`), "Allele Frequency East Asian" = as.numeric(race_frequencies_Sheet2$`Allele Frequency East Asian`),"Allele Frequency European (Finnish)" = as.numeric(race_frequencies_Sheet2$`Allele Frequency European (Finnish)`),"Allele Frequency European (non-Finnish)" = as.numeric(race_frequencies_Sheet2$`Allele Count Frequency European (non-Finnish)`),"Allele Frequency Other" = as.numeric(race_frequencies_Sheet2$`Allele Frequency Other`), "Allele Frequency South Asian" = as.numeric(race_frequencies_Sheet2$`Allele Frequency South Asian`)
```{r x}
data$pop = data$`pop freq. GnomAD`

data$pop[data$`pop freq. GnomAD` <= .000008] <- 0.0
data$pop[data$`pop freq. GnomAD` > .000008 & data$`pop freq. GnomAD` <= .000015] <- 1.0
data$pop[data$`pop freq. GnomAD` > .000015 & data$`pop freq. GnomAD` <= 0.00005] <- 2.0
data$pop[data$`pop freq. GnomAD` > 0.00005] <- 3.0
data$pop <- as.factor(data$pop)
```

```{r graph}
plot1 <- ggplot(data, aes(data$`AA #`, data$`REVEL score`, size = data$`pop freq. GnomAD`))  + geom_point(alpha = 0.5) + labs(x = "AA #", y = "REVEL score", title = "gnomAD REVEL Bubble Plot")  + scale_size(range = c(.1,25), breaks = c(.000008, .000015, 0.00005, 0.0001), guide = guide_legend(title = "Pop Freq"))

par(las = 3)

plot1
```
```{r graph1}
plot1 <- ggplot(data, aes(data$`AA #`, data$`REVEL score`, size = data$`pop freq. GnomAD`))  + geom_point(alpha = 0.5) + labs(x = "AA #", y = "REVEL score", title = "gnomAD REVEL Bubble Plot")  + scale_size_binned(range = c(.1,10), breaks = c(.000008, .000015, 0.00005, 0.0001), guide = guide_legend(title = "Pop Freq"))

par(las = 3)

plot1
```

{r graph1}
plot1 <- ggplot(data, aes(data$`AA #`, data$`REVEL score`, size = data$pop))  + geom_point(alpha = 0.5) + labs(x = "AA #", y = "REVEL score", title = "gnomAD REVEL Bubble Plot") + scale_size(range = c(1.0,10.0), breaks = c(0.0, 1.0, 2.0, 3.0), guide = guide_legend(title = "Pop Freq"))

par(las = 3)

plot1


```{r scale}
data$pop = data$`pop freq. GnomAD`

data$pop[data$`pop freq. GnomAD` <= .000008] <- 0.0
data$pop[data$`pop freq. GnomAD` > .000008 & data$`pop freq. GnomAD` <= .000015] <- 1.0
data$pop[data$`pop freq. GnomAD` > .000015 & data$`pop freq. GnomAD` <= 0.00005] <- 2.0
data$pop[data$`pop freq. GnomAD` > 0.00005] <- 3.0
data$pop <- as.factor(data$pop)
```

```{r}
plot1 <- ggplot(data, aes(data$`AA #`, data$`REVEL score`, size = data$`pop freq. GnomAD`))  + geom_point(alpha = 0.5) + labs(x = "AA #", y = "REVEL score", title = "gnomAD REVEL Bubble Plot")  + scale_size(range = c(.1,25), breaks = c(.000008, .000015, 0.00005, 0.0001), guide = guide_legend(title = "Pop Freq"))

par(las = 3)

plot1
```

{r graph1}
plot1 <- ggplot(data, aes(data$`AA #`, data$`REVEL score`, size = data$pop))  + geom_point(alpha = 0.5) + labs(x = "AA #", y = "REVEL score", title = "gnomAD REVEL Bubble Plot") + scale_size(range = c(1.0,10.0), breaks = c(0.0, 1.0, 2.0, 3.0), guide = guide_legend(title = "Pop Freq"))

par(las = 3)

plot1



{r graph2}
plot1 <- ggplot(data, aes(data$`AA #`, data$`REVEL score`, size = data$pop))  + geom_point(alpha = 0.5) + labs(x = "AA #", y = "REVEL score", title = "gnomAD REVEL Bubble Plot") + scale_size(range = c(1,10), breaks = c(0, 1, 2, 3), guide = guide_legend(title = "Pop Freq"))

par(las = 3)

plot1

```{r more-data}
LRRK2_gnomAD_frequencies_For_figure1 <- read_csv("LRRK2 gnomAD frequencies - Sheet1.csv")

data1 <- LRRK2_gnomAD_frequencies_For_figure1 %>% mutate("AA #" = as.numeric(LRRK2_gnomAD_frequencies_For_figure1$`AA position`), "REVEL score" = as.numeric(LRRK2_gnomAD_frequencies_For_figure1$`REVEL`), Model = rownames(data))
```






```{r new}
mybreaks <-c(0.005, 0.046, 0.23,1.0)
myfix <- c(10.0,20.0,60.0,100.0)

fig_plot <- data %>%
  arrange(desc(data$`pop freq. GnomAD`)) %>%
  mutate(freq = as.numeric(data$`pop freq. GnomAD`)) %>%
ggplot(aes(x = data$`AA #`, y = data$`REVEL score`, size = freq)) + scale_size(range = c(10,80.0), breaks = mybreaks, name = "Frequency") + geom_point(alpha = 0.5) + scale_y_continuous(name = "REVEL score", limits = c(0,1)) + scale_x_continuous(name = "Amino Acid Number", limits = c(0,2527)) + theme(legend.title = element_text(size = 20), legend.text = element_text(size = 20)) + xlab("Amino Acid Number") + labs(title = "gnnomAD AA vs. REVEL with Freq") + ggsave("bubble_gnomAD.pdf", width = 35.0, height = 20.0, limitsize = FALSE)

par(las = 3)

fig_plot
```


```{r inter}
pl<- data1 %>%
  mutate(text = paste("Mutation: ", mutation_code, "\nFrequency: ", data1$`pop freq. GnomAD`, "\nREVEL score: ", REVEL, sep = "")) %>%
  ggplot(aes(x = data1$`AA #`, y = data1$`REVEL score`, size = data1$`pop freq. GnomAD`, text = text)) + scale_size(range = c(3.0,80.0), breaks = mybreaks, name = "Frequency") + scale_y_continuous(name = "REVEL score", limits = c(0,1)) + scale_x_continuous(name = "Amino Acid Number", limits = c(0,2527)) + theme(legend.title = element_text(size = 20), legend.text = element_text(size = 20)) + xlab("Amino Acid Number") + labs(title = "gnnomAD AA vs. REVEL with Freq") + geom_point(alpha = 0.5) + ggsave("bubble.pdf", width = 25, height = 15, limitsize = FALSE)

pl

pp <- ggplotly(pl, tooltip = "text")
pp

saveWidget(pp, file = paste0("ggplotlyBubbleChart.html"))


```


## allele frequencies have different rounding points so use more accurate allele freq (.y)
# merge two data frames by ID
total <- merge(data1, gnomAD_v2_1_1_all_missense ,by= c("Protein Consequence", "Allele Number", "Transcript Consequence", "Allele Count", "Homozygote Count"))

final <- merge(RevRace, race_frequencies_Sheet1, by = c("REVEL score", "Allele Frequency African", "Allele Frequency African", "Allele Frequency South Asian", "Allele Frequency Other", "Allele Count Frequency European (non-Finnish)", "Allele Frequency European (Finnish)", "Allele Frequency East Asian", "Allele Frequency Ashkenazi Jewish"))




## race frequency


```{r}
mybreaks <-c(0.005, 0.046, 0.23,1.0)
myfix <- c(10.0,20.0,60.0,100.0)
mycol <- c('#EF5350', '#EC407A', '#2CD931', '#5E35B1', '#2CD9D1', '#2196F3', '#263238', '#00796B', '#FBC02D')
mybreakscol <-c(0.00, 0.5, 1.0)

#, color = race_frequencies_Sheet1$`Allele Frequency Latino`)

fig_plot1 <- race_frequencies_Sheet_final %>%
  mutate(text = paste("Mutation: ", race_frequencies_Sheet_final$mutation_code, "\nFrequency: ", race_frequencies_Sheet_final$`pop freq. GnomAD`, "\nREVEL score: ", race_frequencies_Sheet_final$REVEL,"\nRace: ", race_frequencies_Sheet_final$Race, sep = "")) %>%
  arrange(desc(race_frequencies_Sheet_final$`Allele Frequency.y`)) %>%
  mutate(freq = as.numeric(race_frequencies_Sheet_final$`Allele Frequency.y`)) %>%
ggplot(aes(x = race_frequencies_Sheet_final$`AA #`, y = race_frequencies_Sheet_final$`REVEL score`, size = freq, color = race_frequencies_Sheet_final$`Race`, text = text)) + scale_size(range = c(3.0,80.0), breaks = mybreaks, name = "Frequency") + scale_y_continuous(name = "REVEL score", limits = c(0,1)) + scale_x_continuous(name = "Amino Acid Number", limits = c(0,2527)) + scale_color_manual(values = mycol, name = "Race") + theme(legend.title = element_text(size = 15), legend.text = element_text(size = 15)) + xlab("Amino Acid Number") + labs(title = "gnomAD AA vs. REVEL with Freq")+geom_point(alpha = 0.5) + ggsave("bubble_race_frequency.pdf", width = 25, height = 15, limitsize = FALSE)

par(las = 3)

fig_plot1
```

```{r}
  
inter1 <- ggplotly(fig_plot1, tooltip = "text", width = 1000, height = 500)
inter1

saveWidget(inter1, file = paste0("BubbleChartRaceFreq.html"))

```





 ggsave("bubble_gnomAD_total.pdf", width = 35.0, height = 20.0, limitsize = FALSE) + 

```{r intero}
pl<- data1 %>%
  mutate(text = paste("Mutation: ", mutation_code, "\nFrequency: ", data1$`pop freq. GnomAD`, "\nREVEL score: ", REVEL, sep = "")) %>%
  ggplot(aes(x = data1$`AA #`, y = data1$`REVEL score`, size = data1$`pop freq. GnomAD`, text = text)) + scale_size(range = c(3.0,80.0), breaks = mybreaks, name = "Frequency") + scale_y_continuous(name = "REVEL score", limits = c(0,1)) + scale_x_continuous(name = "Amino Acid Number", limits = c(0,2527)) + theme(legend.title = element_text(size = 20), legend.text = element_text(size = 20)) + xlab("Amino Acid Number") + labs(title = "gnnomAD AA vs. REVEL with Freq") + geom_point(alpha = 0.5)

pl

pp <- ggplotly(pl, tooltip = "text")
pp

saveWidget(pp, file = paste0("ggplotlyBubbleChart.html"))


```


